cardinalR: Generating interesting high-dimensional data structures

### 2025-04-25 paper-cardinalR.Rmd
Initial work of adding layouts

```{r load-libraries}
library(cardinalR)
library(tidyverse)
library(kableExtra)
library(geozoo)
```

@@

>>>>

```{r load-libraries}
library(cardinalR)
library(tidyverse)
library(kableExtra)
library(geozoo)
library(patchwork)
```

```{r}
#| label: plot-theme
theme_set(theme_linedraw() +
   theme(
     #aspect.ratio = 1,
     plot.background = element_rect(fill = 'transparent', colour = NA),
     plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
     panel.background = element_rect(fill = 'transparent', 
                                     colour = NA),
     panel.grid.major = element_blank(), 
     panel.grid.minor = element_blank(), 
     axis.title.x = element_blank(), axis.title.y = element_blank(),
     axis.text.x = element_blank(), axis.ticks.x = element_blank(),
     axis.text.y = element_blank(), axis.ticks.y = element_blank(),
     legend.background = element_rect(fill = 'transparent', 
                                      colour = NA),
     legend.key = element_rect(fill = 'transparent', 
                               colour = NA),
     legend.position = "bottom", 
     legend.title = element_blank(), 
     legend.text = element_text(size=4),
     legend.key.height = unit(0.25, 'cm'),
     legend.key.width = unit(0.25, 'cm')
   )
)
```

```{r}
interior_annotation <- function(label, position = c(0.92, 0.92), cex = 1, col="grey70") {
  annotation_custom(grid::textGrob(label = label,
                                   x = unit(position[1], "npc"), y = unit(position[2], "npc"),
                                   gp = grid::gpar(cex = cex, col=col)))
}
```

@@

```{r layouts}
tsne_data <- read_rds("data/five_clusts/five_clusts_tsne_perplexity_30.rds")

nldr1 <- tsne_data |>
  ggplot(aes(x = tSNE1,
             y = tSNE2))+
  geom_point(alpha=0.1, size=1, colour='#000000') +
  interior_annotation("a", c(0.08, 0.93)) +
  theme(aspect.ratio = 1)

umap_data <- read_rds("data/five_clusts/five_clusts_umap_n-neigbors_15_min-dist_0.1.rds")

nldr2 <- umap_data |>
  ggplot(aes(x = UMAP1,
             y = UMAP2))+
  geom_point(alpha=0.1, size=1, colour='#000000') +
  interior_annotation("b", c(0.08, 0.93)) +
  theme(aspect.ratio = 1)

phate_data <- read_rds("data/five_clusts/five_clusts_phate_knn_5.rds")

nldr3 <- phate_data |>
  ggplot(aes(x = PHATE1,
             y = PHATE2))+
  geom_point(alpha=0.1, size=1, colour='#000000') +
  interior_annotation("c", c(0.08, 0.93)) +
  theme(aspect.ratio = 1)

trimap_data <- read_rds("data/five_clusts/five_clusts_trimap_n-inliers_12_n-outliers_4_n-random_3.rds")

nldr4 <- trimap_data |>
  ggplot(aes(x = TriMAP1,
             y = TriMAP2))+
  geom_point(alpha=0.1, size=1, colour='#000000') +
  interior_annotation("d", c(0.08, 0.93)) +
  theme(aspect.ratio = 1)

pacmap_data <- read_rds("data/five_clusts/five_clusts_pacmap_n-neighbors_10_init_random_MN-ratio_0.5_FP-ratio_2.rds")

nldr5 <- pacmap_data |>
  ggplot(aes(x = PaCMAP1,
             y = PaCMAP2))+
  geom_point(alpha=0.1, size=1, colour='#000000') +
  interior_annotation("e", c(0.08, 0.93)) +
  theme(aspect.ratio = 1)

pca_data <- read_rds("data/five_clusts/five_clusts_pca.rds")

nldr6 <- pca_data |>
  ggplot(aes(x = pca1,
             y = pca2))+
  geom_point(alpha=0.1, size=1, colour='#000000') +
  interior_annotation("f", c(0.08, 0.93)) +
  theme(aspect.ratio = 1) 
```

```{r}
nldr1 + nldr2 + nldr3 +
  nldr4 + nldr5 + nldr6 +
  plot_layout(ncol = 3)
```
